### 2024-01-17 Paper/paper.tex
init paper

\documentclass[sigconf,natbib=false]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
	\providecommand\BibTeX{{%
			Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
%\setcopyright{acmlicensed}
%\copyrightyear{2018}
%\acmYear{2018}
%\acmDOI{XXXXXXX.XXXXXXX}

%% Bibliography style
\RequirePackage[datamodel=acmdatamodel,style=acmnumeric]{biblatex}

%% Declare bibliography sources
\addbibresource{reference.bib}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

	%%
	%% The "title" command has an optional parameter,
	%% allowing the author to define a "short title" to be used in page headers.
	\title{Assistant tools for blind people playing games}

	\author{Marco Prescher}
	%\authornote{This is a author note!}
	\affiliation{%
		\institution{FHV University of Applied Sciences}
		\streetaddress{Hochschulstraße 1}
		\city{Dornbirn}
		\state{Vorarlberg}
		\country{Austria}}
		\postcode{6850}
	\email{marco.prescher@students.fhv.at}

	%%
	%% By default, the full list of authors will be used in the page
	%% headers. Often, this list is too long, and will overlap
	%% other information printed in the page headers. This command allows
	%% the author to define a more concise list
	%% of authors' names for this purpose.
	\renewcommand{\shortauthors}{Trovato et al.}

	%%
	%% The abstract is a short summary of the work to be presented in the
	%% article.
	%TODO
	\begin{abstract}
		Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
		malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
		sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
		vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
		lacinia dolor. Integer ultricies commodo sem nec semper.
	\end{abstract}

	\ccsdesc[500]{Applied computing~Computer games}
	\ccsdesc[500]{Human-centered computing~Accessibility}
	\ccsdesc[500]{Human computer interaction (HCI)}

	%%
	%% Keywords. The author(s) should pick words that accurately describe
	%% the work being presented. Separate the keywords with commas.
	\keywords{blind, accessibility, gaming, digital games, navigation, tools, AI}

	%TODO?
	%\received{20 February 2007}
	%\received[revised]{12 March 2009}
	%\received[accepted]{5 June 2009}

	%%
	%% This command processes the author and affiliation and title
	%% information and builds the first part of the formatted document.
	\maketitle

	\section{Introduction}
	%TODO
	Short summary of zelda cane article and what i want to expore more!

	\section{Related Work}
	%TODO
	Maybe short summary of the related works i gatherd (State of the art)

	\section{Conclusion}
	%TODO
	\cite{westland_cost_2002}

	%%
	%% Print the bibliography
	%%
	\printbibliography

\end{document}

### 2024-01-17 Paper/template/sample-sigconf-biblatex.tex
init paper

%%
%% This is file `sample-sigconf-biblatex.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% samples.dtx  (with options: `sigconf-biblatex')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from sample-sigconf-biblatex.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file samples.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)
%%
%%
%% Commands for TeXCount
%TC:macro \cite [option:text,text]
%TC:macro \citep [option:text,text]
%TC:macro \citet [option:text,text]
%TC:envir table 0 1
%TC:envir table* 0 1
%TC:envir tabular [ignore] word
%TC:envir displaymath 0 word
%TC:envir math 0 word
%TC:envir comment 0 0
%%
%%
%% The first command in your LaTeX source must be the \documentclass
%% command.
%%
%% For submission and review of your manuscript please change the
%% command to \documentclass[manuscript, screen, review]{acmart}.
%%
%% When submitting camera ready or to TAPS, please change the command
%% to \documentclass[sigconf]{acmart} or whichever template is required
%% for your publication.
%%
%%
\documentclass[sigconf,natbib=false]{acmart}

%%
%% \BibTeX command to typeset BibTeX logo in the docs
\AtBeginDocument{%
	\providecommand\BibTeX{{%
			Bib\TeX}}}

%% Rights management information.  This information is sent to you
%% when you complete the rights form.  These commands have SAMPLE
%% values in them; it is your responsibility as an author to replace
%% the commands and values with those provided to you when you
%% complete the rights form.
\setcopyright{acmlicensed}
\copyrightyear{2018}
\acmYear{2018}
\acmDOI{XXXXXXX.XXXXXXX}

%%
%% Submission ID.
%% Use this when submitting an article to a sponsored event. You'll
%% receive a unique submission ID from the organizers
%% of the event, and this ID should be used as the parameter to this command.
%%\acmSubmissionID{123-A56-BU3}

%%
%% For managing citations, it is recommended to use bibliography
%% files in BibTeX format.
%%
%% You can then either use BibTeX with the ACM-Reference-Format style,
%% or BibLaTeX with the acmnumeric or acmauthoryear sytles, that include
%% support for advanced citation of software artefact from the
%% biblatex-software package, also separately available on CTAN.
%%
%% Look at the sample-*-biblatex.tex files for templates showcasing
%% the biblatex styles.
%%

%%
%% The majority of ACM publications use numbered citations and
%% references, obtained by selecting the acmnumeric BibLaTeX style.
%% The acmauthoryear BibLaTeX style switches to the "author year" style.
%%
%% If you are preparing content for an event
%% sponsored by ACM SIGGRAPH, you must use the acmauthoryear style of
%% citations and references.
%%
%% Bibliography style
\RequirePackage[
datamodel=acmdatamodel,
style=acmnumeric,
]{biblatex}

%% Declare bibliography sources (one \addbibresource command per source)
\addbibresource{software.bib}
\addbibresource{sample-base.bib}

%%
%% end of the preamble, start of the body of the document source.
\begin{document}

	%%
	%% The "title" command has an optional parameter,
	%% allowing the author to define a "short title" to be used in page headers.
	\title{The Name of the Title Is Hope}

	%%
	%% The "author" command and its associated commands are used to define
	%% the authors and their affiliations.
	%% Of note is the shared affiliation of the first two authors, and the
	%% "authornote" and "authornotemark" commands
	%% used to denote shared contribution to the research.
	\author{Ben Trovato}
	\authornote{Both authors contributed equally to this research.}
	\email{trovato@corporation.com}
	\orcid{1234-5678-9012}
	\author{G.K.M. Tobin}
	\authornotemark[1]
	\email{webmaster@marysville-ohio.com}
	\affiliation{%
		\institution{Institute for Clarity in Documentation}
		\streetaddress{P.O. Box 1212}
		\city{Dublin}
		\state{Ohio}
		\country{USA}
		\postcode{43017-6221}
	}

	\author{Lars Th{\o}rv{\"a}ld}
	\affiliation{%
		\institution{The Th{\o}rv{\"a}ld Group}
		\streetaddress{1 Th{\o}rv{\"a}ld Circle}
		\city{Hekla}
		\country{Iceland}}
	\email{larst@affiliation.org}

	\author{Valerie B\'eranger}
	\affiliation{%
		\institution{Inria Paris-Rocquencourt}
		\city{Rocquencourt}
		\country{France}
	}

	\author{Aparna Patel}
	\affiliation{%
		\institution{Rajiv Gandhi University}
		\streetaddress{Rono-Hills}
		\city{Doimukh}
		\state{Arunachal Pradesh}
		\country{India}}

	\author{Huifen Chan}
	\affiliation{%
		\institution{Tsinghua University}
		\streetaddress{30 Shuangqing Rd}
		\city{Haidian Qu}
		\state{Beijing Shi}
		\country{China}}

	\author{Charles Palmer}
	\affiliation{%
		\institution{Palmer Research Laboratories}
		\streetaddress{8600 Datapoint Drive}
		\city{San Antonio}
		\state{Texas}
		\country{USA}
		\postcode{78229}}
	\email{cpalmer@prl.com}

	\author{John Smith}
	\affiliation{%
		\institution{The Th{\o}rv{\"a}ld Group}
		\streetaddress{1 Th{\o}rv{\"a}ld Circle}
		\city{Hekla}
		\country{Iceland}}
	\email{jsmith@affiliation.org}

	\author{Julius P. Kumquat}
	\affiliation{%
		\institution{The Kumquat Consortium}
		\city{New York}
		\country{USA}}
	\email{jpkumquat@consortium.net}

	%%
	%% By default, the full list of authors will be used in the page
	%% headers. Often, this list is too long, and will overlap
	%% other information printed in the page headers. This command allows
	%% the author to define a more concise list
	%% of authors' names for this purpose.
	\renewcommand{\shortauthors}{Trovato et al.}

	%%
	%% The abstract is a short summary of the work to be presented in the
	%% article.
	\begin{abstract}
		A clear and well-documented \LaTeX\ document is presented as an
		article formatted for publication by ACM in a conference proceedings
		or journal publication. Based on the ``acmart'' document class, this
		article presents and explains many of the common variations, as well
		as many of the formatting elements an author may use in the
		preparation of the documentation of their work.
	\end{abstract}

	%%
	%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
	%% Please copy and paste the code instead of the example below.
	%%
	\begin{CCSXML}
		<ccs2012>
		<concept>
		<concept_id>00000000.0000000.0000000</concept_id>
		<concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
		<concept_significance>500</concept_significance>
		</concept>
		<concept>
		<concept_id>00000000.00000000.00000000</concept_id>
		<concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
		<concept_significance>300</concept_significance>
		</concept>
		<concept>
		<concept_id>00000000.00000000.00000000</concept_id>
		<concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
		<concept_significance>100</concept_significance>
		</concept>
		<concept>
		<concept_id>00000000.00000000.00000000</concept_id>
		<concept_desc>Do Not Use This Code, Generate the Correct Terms for Your Paper</concept_desc>
		<concept_significance>100</concept_significance>
		</concept>
		</ccs2012>
	\end{CCSXML}

	\ccsdesc[500]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
	\ccsdesc[300]{Do Not Use This Code~Generate the Correct Terms for Your Paper}
	\ccsdesc{Do Not Use This Code~Generate the Correct Terms for Your Paper}
	\ccsdesc[100]{Do Not Use This Code~Generate the Correct Terms for Your Paper}

	%%
	%% Keywords. The author(s) should pick words that accurately describe
	%% the work being presented. Separate the keywords with commas.
	\keywords{Do, Not, Us, This, Code, Put, the, Correct, Terms, for,
		Your, Paper}

	\received{20 February 2007}
	\received[revised]{12 March 2009}
	\received[accepted]{5 June 2009}

	%%
	%% This command processes the author and affiliation and title
	%% information and builds the first part of the formatted document.
	\maketitle

	\section{Introduction}
	ACM's consolidated article template, introduced in 2017, provides a
	consistent \LaTeX\ style for use across ACM publications, and
	incorporates accessibility and metadata-extraction functionality
	necessary for future Digital Library endeavors. Numerous ACM and
	SIG-specific \LaTeX\ templates have been examined, and their unique
	features incorporated into this single new template.

	If you are new to publishing with ACM, this document is a valuable
	guide to the process of preparing your work for publication. If you
	have published with ACM before, this document provides insight and
	instruction into more recent changes to the article template.

	The ``\verb|acmart|'' document class can be used to prepare articles
	for any ACM publication --- conference or journal, and for any stage
	of publication, from review to final ``camera-ready'' copy, to the
	author's own version, with {\itshape very} few changes to the source.

	\section{Template Overview}
	As noted in the introduction, the ``\verb|acmart|'' document class can
	be used to prepare many different kinds of documentation --- a
	double-anonymous initial submission of a full-length technical paper, a
	two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
	journal article, a SIGCHI Extended Abstract, and more --- all by
	selecting the appropriate {\itshape template style} and {\itshape
		template parameters}.

	This document will explain the major features of the document
	class. For further information, the {\itshape \LaTeX\ User's Guide} is
	available from
	\url{https://www.acm.org/publications/proceedings-template}.

	\subsection{Template Styles}

	The primary parameter given to the ``\verb|acmart|'' document class is
	the {\itshape template style} which corresponds to the kind of publication
	or SIG publishing the work. This parameter is enclosed in square
	brackets and is a part of the {\verb|documentclass|} command:
	\begin{verbatim}
		\documentclass[STYLE]{acmart}
	\end{verbatim}

	Journals use one of three template styles. All but three ACM journals
	use the {\verb|acmsmall|} template style:
	\begin{itemize}
		\item {\texttt{acmsmall}}: The default journal template style.
		\item {\texttt{acmlarge}}: Used by JOCCH and TAP.
		\item {\texttt{acmtog}}: Used by TOG.
	\end{itemize}

	The majority of conference proceedings documentation will use the {\verb|acmconf|} template style.
	\begin{itemize}
		\item {\texttt{sigconf}}: The default proceedings template style.
		\item{\texttt{sigchi}}: Used for SIGCHI conference articles.
		\item{\texttt{sigplan}}: Used for SIGPLAN conference articles.
	\end{itemize}

	\subsection{Template Parameters}

	In addition to specifying the {\itshape template style} to be used in
	formatting your work, there are a number of {\itshape template parameters}
	which modify some part of the applied template style. A complete list
	of these parameters can be found in the {\itshape \LaTeX\ User's Guide.}

	Frequently-used parameters, or combinations of parameters, include:
	\begin{itemize}
		\item {\texttt{anonymous,review}}: Suitable for a ``double-anonymous''
		conference submission. Anonymizes the work and includes line
		numbers. Use with the \texttt{\acmSubmissionID} command to print the
		submission's unique ID on each page of the work.
		\item{\texttt{authorversion}}: Produces a version of the work suitable
		for posting by the author.
		\item{\texttt{screen}}: Produces colored hyperlinks.
	\end{itemize}

	This document uses the following string as the first command in the
	source file:
	\begin{verbatim}
	\end{verbatim}

	\section{Modifications}

	Modifying the template --- including but not limited to: adjusting
	margins, typeface sizes, line spacing, paragraph and list definitions,
	and the use of the \verb|\vspace| command to manually adjust the
	vertical spacing between elements of your work --- is not allowed.

	{\bfseries Your document will be returned to you for revision if
		modifications are discovered.}

	\section{Typefaces}

	The ``\verb|acmart|'' document class requires the use of the
	``Libertine'' typeface family. Your \TeX\ installation should include
	this set of packages. Please do not substitute other typefaces. The
	``\verb|lmodern|'' and ``\verb|ltimes|'' packages should not be used,
	as they will override the built-in typeface families.

	\section{Title Information}

	The title of your work should use capital letters appropriately -
	\url{https://capitalizemytitle.com/} has useful rules for
	capitalization. Use the {\verb|title|} command to define the title of
	your work. If your work has a subtitle, define it with the
	{\verb|subtitle|} command.  Do not insert line breaks in your title.

	If your title is lengthy, you must define a short version to be used
	in the page headers, to prevent overlapping text. The \verb|title|
	command has a ``short title'' parameter:
	\begin{verbatim}
		\title[short title]{full title}
	\end{verbatim}

	\section{Authors and Affiliations}

	Each author must be defined separately for accurate metadata
	identification.  As an exception, multiple authors may share one
	affiliation. Authors' names should not be abbreviated; use full first
	names wherever possible. Include authors' e-mail addresses whenever
	possible.

	Grouping authors' names or e-mail addresses, or providing an ``e-mail
	alias,'' as shown below, is not acceptable:
	\begin{verbatim}
		\author{Brooke Aster, David Mehldau}
		\email{dave,judy,steve@university.edu}
		\email{firstname.lastname@phillips.org}
	\end{verbatim}

	The \verb|authornote| and \verb|authornotemark| commands allow a note
	to apply to multiple authors --- for example, if the first two authors
	of an article contributed equally to the work.

	If your author list is lengthy, you must define a shortened version of
	the list of authors to be used in the page headers, to prevent
	overlapping text. The following command should be placed just after
	the last \verb|\author{}| definition:
	\begin{verbatim}
		\renewcommand{\shortauthors}{McCartney, et al.}
	\end{verbatim}
	Omitting this command will force the use of a concatenated list of all
	of the authors' names, which may result in overlapping text in the
	page headers.

	The article template's documentation, available at
	\url{https://www.acm.org/publications/proceedings-template}, has a
	complete explanation of these commands and tips for their effective
	use.

	Note that authors' addresses are mandatory for journal articles.

	\section{Rights Information}

	Authors of any work published by ACM will need to complete a rights
	form. Depending on the kind of work, and the rights management choice
	made by the author, this may be copyright transfer, permission,
	license, or an OA (open access) agreement.

	Regardless of the rights management choice, the author will receive a
	copy of the completed rights form once it has been submitted. This
	form contains \LaTeX\ commands that must be copied into the source
	document. When the document source is compiled, these commands and
	their parameters add formatted text to several areas of the final
	document:
	\begin{itemize}
		\item the ``ACM Reference Format'' text on the first page.
		\item the ``rights management'' text on the first page.
		\item the conference information in the page header(s).
	\end{itemize}

	Rights information is unique to the work; if you are preparing several
	works for an event, make sure to use the correct set of commands with
	each of the works.

	The ACM Reference Format text is required for all articles over one
	page in length, and is optional for one-page articles (abstracts).

	\section{CCS Concepts and User-Defined Keywords}

	Two elements of the ``acmart'' document class provide powerful
	taxonomic tools for you to help readers find your work in an online
	search.

	The ACM Computing Classification System ---
	\url{https://www.acm.org/publications/class-2012} --- is a set of
	classifiers and concepts that describe the computing
	discipline. Authors can select entries from this classification
	system, via \url{https://dl.acm.org/ccs/ccs.cfm}, and generate the
	commands to be included in the \LaTeX\ source.

	User-defined keywords are a comma-separated list of words and phrases
	of the authors' choosing, providing a more flexible way of describing
	the research being presented.

	CCS concepts and user-defined keywords are required for for all
	articles over two pages in length, and are optional for one- and
	two-page articles (or abstracts).

	\section{Sectioning Commands}

	Your work should use standard \LaTeX\ sectioning commands:
	\verb|section|, \verb|subsection|, \verb|subsubsection|, and
	\verb|paragraph|. They should be numbered; do not remove the numbering
	from the commands.

	Simulating a sectioning command by setting the first word or words of
	a paragraph in boldface or italicized text is {\bfseries not allowed.}

	\section{Tables}

	The ``\verb|acmart|'' document class includes the ``\verb|booktabs|''
	package --- \url{https://ctan.org/pkg/booktabs} --- for preparing
	high-quality tables.

	Table captions are placed {\itshape above} the table.

	Because tables cannot be split across pages, the best placement for
	them is typically the top of the page nearest their initial cite.  To
	ensure this proper ``floating'' placement of tables, use the
	environment \textbf{table} to enclose the table's contents and the
	table caption.  The contents of the table itself must go in the
	\textbf{tabular} environment, to be aligned properly in rows and
	columns, with the desired horizontal and vertical rules.  Again,
	detailed instructions on \textbf{tabular} material are found in the
	\textit{\LaTeX\ User's Guide}.

	Immediately following this sentence is the point at which
	Table~\ref{tab:freq} is included in the input file; compare the
	placement of the table here with the table in the printed output of
	this document.

	\begin{table}
		\caption{Frequency of Special Characters}
		\label{tab:freq}
		\begin{tabular}{ccl}
			\toprule
			Non-English or Math&Frequency&Comments\\
			\midrule
			\O & 1 in 1,000& For Swedish names\\
			$\pi$ & 1 in 5& Common in math\\
			\$ & 4 in 5 & Used in business\\
			$\Psi^2_1$ & 1 in 40,000& Unexplained usage\\
			\bottomrule
		\end{tabular}
	\end{table}

	To set a wider table, which takes up the whole width of the page's
	live area, use the environment \textbf{table*} to enclose the table's
	contents and the table caption.  As with a single-column table, this
	wide table will ``float'' to a location deemed more
	desirable. Immediately following this sentence is the point at which
	Table~\ref{tab:commands} is included in the input file; again, it is
	instructive to compare the placement of the table here with the table
	in the printed output of this document.

	\begin{table*}
		\caption{Some Typical Commands}
		\label{tab:commands}
		\begin{tabular}{ccl}
			\toprule
			Command &A Number & Comments\\
			\midrule
			\texttt{{\char'134}author} & 100& Author \\
			\texttt{{\char'134}table}& 300 & For tables\\
			\texttt{{\char'134}table*}& 400& For wider tables\\
			\bottomrule
		\end{tabular}
	\end{table*}

	Always use midrule to separate table header rows from data rows, and
	use it only for this purpose. This enables assistive technologies to
	recognise table headers and support their users in navigating tables
	more easily.

	\section{Math Equations}
	You may want to display math equations in three distinct styles:
	inline, numbered or non-numbered display.  Each of the three are
	discussed in the next sections.

	\subsection{Inline (In-text) Equations}
	A formula that appears in the running text is called an inline or
	in-text formula.  It is produced by the \textbf{math} environment,
	which can be invoked with the usual
	\texttt{{\char'134}begin\,\ldots{\char'134}end} construction or with
	the short form \texttt{\$\,\ldots\$}. You can use any of the symbols
	and structures, from $\alpha$ to $\omega$, available in
	\LaTeX~\cite{Lamport:LaTeX}; this section will simply show a few
	examples of in-text equations in context. Notice how this equation:
	\begin{math}
		\lim_{n\rightarrow \infty}x=0
	\end{math},
	set here in in-line math style, looks slightly different when
	set in display style.  (See next section).

	\subsection{Display Equations}
	A numbered display equation---one set off by vertical space from the
	text and centered horizontally---is produced by the \textbf{equation}
	environment. An unnumbered display equation is produced by the
	\textbf{displaymath} environment.

	Again, in either environment, you can use any of the symbols and
	structures available in \LaTeX\@; this section will just give a couple
	of examples of display equations in context.  First, consider the
	equation, shown as an inline equation above:
	\begin{equation}
		\lim_{n\rightarrow \infty}x=0
	\end{equation}
	Notice how it is formatted somewhat differently in
	the \textbf{displaymath}
	environment.  Now, we'll enter an unnumbered equation:
	\begin{displaymath}
		\sum_{i=0}^{\infty} x + 1
	\end{displaymath}
	and follow it with another numbered equation:
	\begin{equation}
		\sum_{i=0}^{\infty}x_i=\int_{0}^{\pi+2} f
	\end{equation}
	just to demonstrate \LaTeX's able handling of numbering.

	\section{Figures}

	The ``\verb|figure|'' environment should be used for figures. One or
	more images can be placed within a figure. If your figure contains
	third-party material, you must clearly identify it as such, as shown
	in the example below.
	\begin{figure}[h]
		\centering
		\includegraphics[width=\linewidth]{sample-franklin}
		\caption{1907 Franklin Model D roadster. Photograph by Harris \&
			Ewing, Inc. [Public domain], via Wikimedia
			Commons. (\url{https://goo.gl/VLCRBB}).}
		\Description{A woman and a girl in white dresses sit in an open car.}
	\end{figure}

	Your figures should contain a caption which describes the figure to
	the reader.

	Figure captions are placed {\itshape below} the figure.

	Every figure should also have a figure description unless it is purely
	decorative. These descriptions convey what’s in the image to someone
	who cannot see it. They are also used by search engine crawlers for
	indexing images, and when images cannot be loaded.

	A figure description must be unformatted plain text less than 2000
	characters long (including spaces).  {\bfseries Figure descriptions
		should not repeat the figure caption – their purpose is to capture
		important information that is not already provided in the caption or
		the main text of the paper.} For figures that convey important and
	complex new information, a short text description may not be
	adequate. More complex alternative descriptions can be placed in an
	appendix and referenced in a short figure description. For example,
	provide a data table capturing the information in a bar chart, or a
	structured list representing a graph.  For additional information
	regarding how best to write figure descriptions and why doing this is
	so important, please see
	\url{https://www.acm.org/publications/taps/describing-figures/}.

	\subsection{The ``Teaser Figure''}

	A ``teaser figure'' is an image, or set of images in one figure, that
	are placed after all author and affiliation information, and before
	the body of the article, spanning the page. If you wish to have such a
	figure in your article, place the command immediately before the
	\verb|\maketitle| command:
	\begin{verbatim}
		\begin{teaserfigure}
			\includegraphics[width=\textwidth]{sampleteaser}
			\caption{figure caption}
			\Description{figure description}
		\end{teaserfigure}
	\end{verbatim}

	\section{Citations and Bibliographies}

	The use of \BibTeX\ for the preparation and formatting of one's
	references is strongly recommended. Authors' names should be complete
	--- use full first names (``Donald E. Knuth'') not initials
	(``D. E. Knuth'') --- and the salient identifying features of a
	reference should be included: title, year, volume, number, pages,
	article DOI, etc.

	Using the BibLaTeX system, the bibliography is included in your source
	document with the following command, placed just before the \verb|\end{document}| command:
\begin{verbatim}
	\printbibliography
\end{verbatim}

The command \verb|\addbibresource{bibfile}| declares the \BibTeX\ file to use
in the {\bfseries preamble} (before the command
``\verb|\begin{document}|'') of your \LaTeX\ source
	where ``\verb|bibfile|'' is the name, \emph{with} the ``\verb|.bib|'' suffix.
	Notice that \verb|\addbibresource| takes only one argument: to declare multiple files,
	use multiple instances of the command.

	Citations and references are numbered by default. A small number of
	ACM publications have citations and references formatted in the
	``author year'' style; for these exceptions, please pass the option \verb|style=acmauthoryear|
	to the \verb|biblatex| package loaded in the {\bfseries preamble} (before the command
	``\verb|\begin{document}|'') of your \LaTeX\ source.

		Some examples.  A paginated journal article \cite{Abril07}, an
		enumerated journal article \cite{Cohen07}, a reference to an entire
		issue \cite{JCohen96}, a monograph (whole book) \cite{Kosiur01}, a
		monograph/whole book in a series (see 2a in spec. document)
		\cite{Harel79}, a divisible-book such as an anthology or compilation
		\cite{Editor00} followed by the same example, however we only output
		the series if the volume number is given \cite{Editor00a} (so
		Editor00a's series should NOT be present since it has no vol. no.),
		a chapter in a divisible book \cite{Spector90}, a chapter in a
		divisible book in a series \cite{Douglass98}, a multi-volume work as
		book \cite{Knuth97}, a couple of articles in a proceedings (of a
		conference, symposium, workshop for example) (paginated proceedings
		article) \cite{Andler79, Hagerup1993}, a proceedings article with
		all possible elements \cite{Smith10}, an example of an enumerated
		proceedings article \cite{VanGundy07}, an informally published work
		\cite{Harel78}, a couple of preprints \cite{Bornmann2019,
			AnzarootPBM14}, a doctoral dissertation \cite{Clarkson85}, a
		master's thesis: \cite{anisi03}, an online document / world wide web
		resource \cite{Thornburg01, Ablamowicz07, Poker06}, a video game
		(Case 1) \cite{Obama08} and (Case 2) \cite{Novak03} and \cite{Lee05}
		and (Case 3) a patent \cite{JoeScientist001}, work accepted for
		publication \cite{rous08}, 'YYYYb'-test for prolific author
		\cite{SaeediMEJ10} and \cite{SaeediJETC10}. Other cites might
		contain 'duplicate' DOI and URLs (some SIAM articles)
		\cite{Kirschmer:2010:AEI:1958016.1958018}. Boris / Barbara Beeton:
		multi-volume works as books \cite{MR781536} and \cite{MR781537}. A
		couple of citations with DOIs:
		\cite{2004:ITE:1009386.1010128,Kirschmer:2010:AEI:1958016.1958018}. Online
		citations: \cite{TUGInstmem, Thornburg01, CTANacmart}.
		Data Artifacts: \cite{UMassCitations}.
		Software project: ~\cite{cgal,delebecque:hal-02090402}. Software Version: ~\cite{gf-tag-sound-repo,}. Software Module: ~\cite{cgal:lp-gi-20a}. Code fragment: ~\cite{simplemapper}.

		\section{Acknowledgments}

		Identification of funding sources and other support, and thanks to
		individuals and groups that assisted in the research and the
		preparation of the work should be included in an acknowledgment
		section, which is placed just before the reference section in your
		document.

		This section has a special environment:
		\begin{verbatim}
			\begin{acks}
				...
			\end{acks}
		\end{verbatim}
		so that the information contained therein can be more easily collected
		during the article metadata extraction phase, and to ensure
		consistency in the spelling of the section heading.

		Authors should not prepare this section as a numbered or unnumbered {\verb|\section|}; please use the ``{\verb|acks|}'' environment.

		\section{Appendices}

		If your work needs an appendix, add it before the
		``\verb|\end{document}|'' command at the conclusion of your source
	document.

	Start the appendix with the ``\verb|appendix|'' command:
	\begin{verbatim}
		\appendix
	\end{verbatim}
	and note that in the appendix, sections are lettered, not
	numbered. This document has two appendices, demonstrating the section
	and subsection identification method.

	\section{Multi-language papers}

	Papers may be written in languages other than English or include
	titles, subtitles, keywords and abstracts in different languages (as a
	rule, a paper in a language other than English should include an
	English title and an English abstract).  Use \verb|language=...| for
	every language used in the paper.  The last language indicated is the
	main language of the paper.  For example, a French paper with
	additional titles and abstracts in English and German may start with
	the following command
	\begin{verbatim}
		\documentclass[sigconf, language=english, language=german,
		language=french]{acmart}
	\end{verbatim}

	The title, subtitle, keywords and abstract will be typeset in the main
	language of the paper.  The commands \verb|\translatedXXX|, \verb|XXX|
	begin title, subtitle and keywords, can be used to set these elements
	in the other languages.  The environment \verb|translatedabstract| is
	used to set the translation of the abstract.  These commands and
	environment have a mandatory first argument: the language of the
	second argument.  See \verb|sample-sigconf-i13n.tex| file for examples
	of their usage.

	\section{SIGCHI Extended Abstracts}

	The ``\verb|sigchi-a|'' template style (available only in \LaTeX\ and
	not in Word) produces a landscape-orientation formatted article, with
	a wide left margin. Three environments are available for use with the
	``\verb|sigchi-a|'' template style, and produce formatted output in
	the margin:
	\begin{description}
		\item[\texttt{sidebar}:]  Place formatted text in the margin.
		\item[\texttt{marginfigure}:] Place a figure in the margin.
		\item[\texttt{margintable}:] Place a table in the margin.
	\end{description}

	%%
	%% The acknowledgments section is defined using the "acks" environment
	%% (and NOT an unnumbered section). This ensures the proper
	%% identification of the section in the article metadata, and the
	%% consistent spelling of the heading.
	\begin{acks}
		To Robert, for the bagels and explaining CMYK and color spaces.
	\end{acks}

	%%
	%% Print the bibliography
	%%
	\printbibliography

	%%
	%% If your work has an appendix, this is the place to put it.
	\appendix

	\section{Research Methods}

	\subsection{Part One}

	Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
	malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
	sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
	vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
	lacinia dolor. Integer ultricies commodo sem nec semper.

	\subsection{Part Two}

	Etiam commodo feugiat nisl pulvinar pellentesque. Etiam auctor sodales
	ligula, non varius nibh pulvinar semper. Suspendisse nec lectus non
	ipsum convallis congue hendrerit vitae sapien. Donec at laoreet
	eros. Vivamus non purus placerat, scelerisque diam eu, cursus
	ante. Etiam aliquam tortor auctor efficitur mattis.

	\section{Online Resources}

	Nam id fermentum dui. Suspendisse sagittis tortor a nulla mollis, in
	pulvinar ex pretium. Sed interdum orci quis metus euismod, et sagittis
	enim maximus. Vestibulum gravida massa ut felis suscipit
	congue. Quisque mattis elit a risus ultrices commodo venenatis eget
	dui. Etiam sagittis eleifend elementum.

	Nam interdum magna at lectus dignissim, ac dignissim lorem
	rhoncus. Maecenas eu arcu ac neque placerat aliquam. Nunc pulvinar
	massa et mattis lacinia.

\end{document}
\endinput
%%
%% End of file `sample-sigconf-biblatex.tex'.

### 2024-01-17 Paper/paper.tex
removed samples.ins + minor changes
Added minor structure of how I want to write my paper

@@
 	%% allowing the author to define a "short title" to be used in page headers.
-	\title{Assistant tools for blind people playing games}
+	\title{Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games}
 
@@
 	%TODO
-	Short summary of zelda cane article and what i want to expore more!
+	Short summary of \emph{My Zelda Cane} paper about what they wrote and noting that they did not explore general Accessibility Features current game companies are using/developing as well as state-of-the-art tools.
+	In Addition to that I want to explore those tools and Accessibility Features deeper.
+	As Third point I want to get a deeper look into how software companies handle features for blind people like \emph{The Last of Us: Part 2}.
 
-	\section{Related Work}
+	\section{State of the art}
 	%TODO
-	Maybe short summary of the related works i gatherd (State of the art)
+	New tools for blind players and newest Accessibility Features software companies using/developing.
+
+	Screen Reader
+	Audio Cues and Descriptions
+	Haptic Feedback
+	Customizable Controls
+	Text-to-Speech and Speech Recognition
+	Accessible Menus and Interfaces
+	Echolocation
+
+	\section{Get deeper into one or two new tools for blind players}
+	%TODO
+
+	\section{Get deeper into one or two Accessibility Features}
+	%TODO
+
+	\section{Future Work (What else could be done, explored deeper or would benefit blind players)}
+	%TODO
 
@@
 	%TODO
+	Summary of key findings
+
 	\cite{westland_cost_2002}

### 2024-02-11 Paper/paper.tex
Restructured paper and implemented basic "Introduction" chapter

--- 2024-01-17 Paper/paper.tex
@@
-\documentclass[sigconf,natbib=false]{acmart}
+\documentclass[sigconf,natbib=false,9pt]{acmart}
 
@@
 	\section{Introduction}
+	Today's accessible games for blind people are mainly games which are directly developed for them (\textcite{goncalves_my_2023}).
+	While these games are enjoyable, mainstream games are a serious challenge for blind people because they consist of complex environments, mechanics and interactions with \emph{Non-Player Character} (NPC) players or even real players in \emph{Player versus player} (PvP) games.
+
+	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_nodate, playstation_last_nodate-1}. 
+	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced.
+	Additionally, \textcite{dale_last_2024} described that the game can be played all the way through with audio cues and navigation aids.
+	It includes preset accessibility options for common disabilities like hearing or vision impairments. 
+	It also introduces accessibility menus when the game is first started, making it easier for players with disabilities to adjust settings.
+	To top that, \emph{Naughty Dog} released a remastered version of TLOU2 in 2024 with a reworked \emph{Cinematic Audio Descriptions} feature \cite{playstation_last_nodate-2}.
+
+	In this work we go deeper into different and potentially new accessibility features as well as what assistant tools blind players use and how software companies implement them.
+	This raises three relevant research questions (RQ):
+
+	\begin{itemize}
+		\item RQ1: What new breakthrough accessibility features and tools could enhance the gaming experience for blind players?
+		\item RQ2: How can the development and implementation of these features and tools be standardized within the development cycle of visual-centric digital games?
+	\end{itemize}
+
+	\section{The Problem}
 	%TODO
-	Short summary of zelda cane article and what i want to expore more!
+	Summary of findings in "MyZeldaCane" and what current problems with visual centric games are (for blind people).
+	Lack of new tools and features as well as costs for standardized the development cycle to implement those.
+
+	\section{My Idea}
+	%TODO
+	Discuss your proposed idea for addressing the problem identified in the previous section.
+This could involve developing new assistant tools or enhancing existing accessibility features for blind people playing visual-centric digital games.
+Outline the key components of your idea and how it aims to improve the gaming experience for blind players.
+Consider addressing the following points:
+
+	The rationale behind your idea and why it is important.
+	How your idea builds upon existing tools and features.
+	Any innovative approaches or technologies you plan to implement.
+	The potential impact of your idea on blind gamers and the gaming industry as a whole.
+
+	\section{The Details}
+	%TODO
+	New tools for blind players and newest Accessibility Features software companies using/developing.
+
+	Screen Reader
+	Audio Cues and Descriptions
+	Haptic Feedback
+	Customizable Controls
+	Text-to-Speech and Speech Recognition
+	Accessible Menus and Interfaces
+	Echolocation
+
+	Provide a detailed explanation of how your idea will be implemented.
+This section should delve into the technical aspects of your proposed solution and address any challenges or limitations that may arise.
+Consider including the following information:
+
+	The specific features and functionalities of your assistant tools or accessibility features.
+	The technologies or algorithms involved in implementing these features (e.g., machine learning, computer vision).
+	Any hardware or software requirements necessary for your solution to work.
+	How your solution will be integrated into existing digital games or gaming platforms.
+	Any user testing or feedback you have conducted to validate your idea.
 
@@
 	%TODO
-	Maybe short summary of the related works i gatherd (State of the art)
+	Review existing literature and research related to assistant tools and accessibility features for blind gamers.
+This section should provide an overview of the current state-of-the-art in this field and highlight any relevant studies or projects.
+Consider addressing the following points:
 
-	\section{Conclusion}
+	Previous research on accessibility features in digital games for blind players.
+	Existing assistant tools or software developed to improve the gaming experience for blind individuals.
+	Studies or projects that have investigated the challenges faced by blind gamers and potential solutions.
+	Any notable advancements or innovations in the field of accessibility technology for blind users.
+	How your research builds upon or contributes to the existing body of work in this area.
+
+	\section{Conclusions and Further Work}
+	What else could be done, explored deeper or would benefit blind players
 	%TODO
-	\cite{westland_cost_2002}
+	Summarize the key findings and contributions of your research paper.
+Reflect on the significance of your proposed idea and its potential impact on improving accessibility for blind gamers.
+Additionally, discuss any avenues for future research or development in this field.
+Consider addressing the following points:
+
+	A recap of the problem addressed and the proposed solution.
+	The implications of your research for the gaming industry and the broader accessibility community.
+	Any remaining challenges or unanswered questions that need to be addressed.
+	Suggestions for future research directions or enhancements to your proposed idea.
+	How your work contributes to advancing the state-of-the-art in accessibility technology for blind individuals playing digital games.
 

### 2024-02-13 Paper/paper.tex
minor change
added "The Problem" and "My Idea" section

@@
-\documentclass[sigconf,natbib=false,9pt]{acmart}
+\documentclass[sigconf,natbib=false,10pt]{acmart}
 
@@
 	%% of authors' names for this purpose.
-	\renewcommand{\shortauthors}{Trovato et al.}
+	\renewcommand{\shortauthors}{Marco Prescher}
 
@@
 
-	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_nodate, playstation_last_nodate-1}. 
+	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_2020, playstation_last_2020-1}. 
 	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced.
@@
 	It also introduces accessibility menus when the game is first started, making it easier for players with disabilities to adjust settings.
-	To top that, \emph{Naughty Dog} released a remastered version of TLOU2 in 2024 with a reworked \emph{Cinematic Audio Descriptions} feature \cite{playstation_last_nodate-2}.
+	To top that, \emph{Naughty Dog} released a remastered version of TLOU2 in 2024 with a reworked \emph{Cinematic Audio Descriptions} feature \cite{playstation_last_2024}.
 
 	In this work we go deeper into different and potentially new accessibility features as well as what assistant tools blind players use and how software companies implement them.
-	This raises three relevant research questions (RQ):
+	This raises two relevant research questions (RQ):
 
@@
 	\section{The Problem}
-	%TODO
-	Summary of findings in "MyZeldaCane" and what current problems with visual centric games are (for blind people).
-	Lack of new tools and features as well as costs for standardized the development cycle to implement those.
+	Blind players encounter many different barriers when playing visual-centric digital games which often rely greatly on graphical interfaces and visual cues. 
+	To top that, the collection of those mainstream games have different perspectives such as top-down, first-person, and third-person views, where all three views give the player unique challenges in navigating game environment, understanding game objectives and interacting with in-game elements like players or objects.
+	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) which still represent a great challenge for both players and developers.
+
+	\begin{figure*}[ht]
+		\centering
+		\includegraphics[scale=0.6,width=\textwidth]{assets/seven-themes.png}
+		\caption{Seven themes and respective unresolved barriers (Source: \textcite{goncalves_my_2023})}
+		\label{fig:seven-themes}
+	\end{figure*}
+
+	\autoref{fig:seven-themes} gives a great overview what accessibility features and assistant tools are still missing and in which direction the gaming industry should focus.
 
 	\section{My Idea}
-	%TODO
-	Discuss your proposed idea for addressing the problem identified in the previous section.
-This could involve developing new assistant tools or enhancing existing accessibility features for blind people playing visual-centric digital games.
-Outline the key components of your idea and how it aims to improve the gaming experience for blind players.
-Consider addressing the following points:
+	The gaming industry came a long way from no accessibility features and assistant tools at all to implementing more than 60 accessibility features in one game \cite{playstation_last_2020}.
+	According to research papers \cite{goncalves_my_2023, grammenos_designing_2009, grammenos_game_2008, araujo_mobile_2017} some of the most important accessibility features for blind people in visual-centric games include:
 
-	The rationale behind your idea and why it is important.
-	How your idea builds upon existing tools and features.
-	Any innovative approaches or technologies you plan to implement.
-	The potential impact of your idea on blind gamers and the gaming industry as a whole.
+	\begin{itemize}
+		\item Audio Cues and Descriptions
+		\item Text-to-Speech (TTS) and Voiceover
+		\item Navigation Aids and Wayfinding Tools
+		\item Comprehensive Audio Design
+		\item Customizable Controls and Inputs
+		\item Tactile Feedback and Controller Design
+	\end{itemize}
+
+    Some of these have already been implemented to a certain extent in some games, but as \autoref{fig:seven-themes} notes, there are still problems.
+    Especially when it comes to the environment, pathfinding, perspective and interacting with the world, blind players face major challenges, which according to \textcite{goncalves_my_2023} could mean they stop playing these games because they simply can not find the right way to play.
+
+    To address the environment and pathfinding problems, one new technology was introduced in 2018 by \textcite{andrade_echo-house_2018} to use echolocation to explore a virtual environment which could drastically improve navigation in it.
+    As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or AI assistant tools could be a solution when developed and integration further.
+    Whereas the haptic feedback of e.g.
+PS5-Controllers could indicate when players aim too high or too low and the AI-Tool could provide the player with enhanced audio descriptions how to interact with the world.
+
+    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visually-centric digital games are still a major challenge for blind players.
+    In the following section we will delve deeper into the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.
 
 	\section{The Details}
+
+	Subsections for the details section
+	\begin{itemize}
+		\item Universally accessible game design
+		\item Problems implementing accessibility features in digital games
+		\item Cost effective methods to implement accessibility features
+		\item Improve exploring virtual environments using echolocation
+	\end{itemize}
+
 	%TODO

### 2024-02-16 Paper/paper.tex
improved structure and started with the section "The Details"

@@
 
-	In this work we go deeper into different and potentially new accessibility features as well as what assistant tools blind players use and how software companies implement them.
+	Implementing accessibility features is much needed in digital games to ensure that everyone can enjoy gaming.
+	However, game developers in general face various problems in the process of developing games, some of them are:
+
+	\begin{itemize}
+		\setlength\itemsep{0.5em}
+		\item Diverse Needs
+		\item Technical Challenges
+		\item Design Compromises
+		\item Standardization
+	\end{itemize}
+
+	In this study, we explore different and innovative accessibility features and tools, including haptic feedback which is a major technical challenge, design compromises and their associated problems and the need for standardization.
 	This raises two relevant research questions (RQ):
@@
 	\begin{itemize}
-		\item RQ1: What new breakthrough accessibility features and tools could enhance the gaming experience for blind players?
-		\item RQ2: How can the development and implementation of these features and tools be standardized within the development cycle of visual-centric digital games?
+		\setlength\itemsep{0.5em}
+		\item RQ1: Which innovative accessibility features and tools can enhance the gaming experience for blind players?
+		\item RQ2: In what ways can haptic feedback enhancements improve the game experience for blind players?
 	\end{itemize}
@@
 	\begin{itemize}
+		\setlength\itemsep{0.5em}
 		\item Audio Cues and Descriptions
-		\item Text-to-Speech (TTS) and Voiceover
+		\item \emph{Text-to-Speech} (TTS) and Voiceover
 		\item Navigation Aids and Wayfinding Tools
@@
     As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or AI assistant tools could be a solution when developed and integration further.
-    Whereas the haptic feedback of e.g.
-PS5-Controllers could indicate when players aim too high or too low and the AI-Tool could provide the player with enhanced audio descriptions how to interact with the world.
+    Whereas the haptic feedback \cite{bello_haptics_2016} of for example PS5-Controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate when players aim too high or too low while the AI-Tool could provide the player with enhanced audio descriptions and how to interact with the world.
 
     In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visually-centric digital games are still a major challenge for blind players.
-    In the following section we will delve deeper into the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.
+    In the following section we will delve deeper into some of the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.
 
 	\section{The Details}
+	In this section, we delve into enhancing accessibility in digital games for blind players.
+	Firstly, we aim to explore previously mentioned developing problems, from universally accessible game design affecting diverse needs followed by technical challenges.
+	Secondly, we propose enhancements of already existing accessibility features in the theme environment navigating.
+	Lastly, we explore various types of feedback which are essential in enhancing of accessibility in digital games and focus on haptic feedback as well as further possibilities to use that to improve the experience in digital games for blind players.
 
-	Subsections for the details section
-	\begin{itemize}
-		\item Universally accessible game design
-		\item Problems implementing accessibility features in digital games
-		\item Cost effective methods to implement accessibility features
-		\item Improve exploring virtual environments using echolocation
-	\end{itemize}
+	\subsection{Universally accessible game design}
+	%TODO
+	Test
 
+	\subsection{Navigate a virtual environment using echolocation}
 	%TODO
-	New tools for blind players and newest Accessibility Features software companies using/developing.
+	Test
 
-	Screen Reader
-	Audio Cues and Descriptions
-	Haptic Feedback
-	Customizable Controls
-	Text-to-Speech and Speech Recognition
-	Accessible Menus and Interfaces
-	Echolocation
+	\subsection{Assistive haptic feedback}
+	%TODO
+	Short introduction into feedback variants and where it is used "visual perception (sight), haptics (tactile) and aural (hearing)". \cite{kuber_towards_2007}
 
-	Provide a detailed explanation of how your idea will be implemented.
-This section should delve into the technical aspects of your proposed solution and address any challenges or limitations that may arise.
-Consider including the following information:
-
-	The specific features and functionalities of your assistant tools or accessibility features.
-	The technologies or algorithms involved in implementing these features (e.g., machine learning, computer vision).
-	Any hardware or software requirements necessary for your solution to work.
-	How your solution will be integrated into existing digital games or gaming platforms.
-	Any user testing or feedback you have conducted to validate your idea.
+	\subsection{Further possibilities to use haptic feedback}
+	%TODO
+	Test
 
 	\section{Related Work}
-	%TODO
-	Review existing literature and research related to assistant tools and accessibility features for blind gamers.
-This section should provide an overview of the current state-of-the-art in this field and highlight any relevant studies or projects.
-Consider addressing the following points:
+	Accessibility in visual-centric games is getting more important and the game industry have to keep up implementing them.
+	The research paper \textcite{goncalves_my_2023} has shown us that there are still major challenges to improve and further enhance existing accessibility features in various themes.
+	In 2008 \textcite{grammenos_game_2008} developed a game called \emph{Game Over!}, which is the first universally inaccessible game showing people how it is if a game is unplayable.
+	Additionally, in 2018 \textcite{andrade_echo-house_2018} described a new method to explore a virtual environment by using echolocation.
+	This section provides a deeper insight into these studies, how they approached the topic and what results they achieved.
 
-	Previous research on accessibility features in digital games for blind players.
-	Existing assistant tools or software developed to improve the gaming experience for blind individuals.
-	Studies or projects that have investigated the challenges faced by blind gamers and potential solutions.
-	Any notable advancements or innovations in the field of accessibility technology for blind users.
-	How your research builds upon or contributes to the existing body of work in this area.
+	\subsection{Echolocation in games}
+	Test
 
 	\section{Conclusions and Further Work}
-	What else could be done, explored deeper or would benefit blind players
 	%TODO
-	Summarize the key findings and contributions of your research paper.
-Reflect on the significance of your proposed idea and its potential impact on improving accessibility for blind gamers.
-Additionally, discuss any avenues for future research or development in this field.
-Consider addressing the following points:
-
 	A recap of the problem addressed and the proposed solution.

### 2024-02-17 Paper/paper.tex
Added section "Related work" + continued with "The Details"

@@
 
-	%TODO?
 	%\received{20 February 2007}
@@
 
-	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_2020, playstation_last_2020-1}. 
-	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced.
-	Additionally, \textcite{dale_last_2024} described that the game can be played all the way through with audio cues and navigation aids.
-	It includes preset accessibility options for common disabilities like hearing or vision impairments. 
-	It also introduces accessibility menus when the game is first started, making it easier for players with disabilities to adjust settings.
-	To top that, \emph{Naughty Dog} released a remastered version of TLOU2 in 2024 with a reworked \emph{Cinematic Audio Descriptions} feature \cite{playstation_last_2024}.
-
-	Implementing accessibility features is much needed in digital games to ensure that everyone can enjoy gaming.
+	Implementing accessibility features is much needed in digital games to ensure that everyone, including people with disabilities can enjoy gaming.
 	However, game developers in general face various problems in the process of developing games, some of them are:
@@
 
-	In this study, we explore different and innovative accessibility features and tools, including haptic feedback which is a major technical challenge, design compromises and their associated problems and the need for standardization.
+	So, the main idea of this paper is to give a broad insight of different and innovative accessibility features and tools, including haptic feedback and its ways to improve game experience which is a major technical challenge.
+	Additionally, this study explores design compromises and their associated problems as well as the need for standardization in the gaming industry developing games.
 	This raises two relevant research questions (RQ):
@@
 
+	%TODO
+	Contributions...
+
+	\subsection{Motivation}
+	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_2020, playstation_last_2020-1}. 
+	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced.
+	Additionally, \textcite{dale_last_2024} described that the game can be played all the way through with audio cues and navigation aids.
+	It includes preset accessibility options for common disabilities like hearing or vision impairments. 
+	It also introduces accessibility menus when the game is first started, making it easier for players with disabilities to adjust settings.
+	To top that, \emph{Naughty Dog} released a remastered version of TLOU2 in 2024 with a reworked \emph{Cinematic Audio Descriptions} feature \cite{playstation_last_2024}.
+
 	\section{The Problem}
@@
 	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) which still represent a great challenge for both players and developers.
+	%TODO rewrite
 
@@
     As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or AI assistant tools could be a solution when developed and integration further.
-    Whereas the haptic feedback \cite{bello_haptics_2016} of for example PS5-Controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate when players aim too high or too low while the AI-Tool could provide the player with enhanced audio descriptions and how to interact with the world.
+    Whereas the haptic feedback \cite{bello_haptics_2016} of for example PS5-Controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate when players aim too high or too low while an AI tool could provide the player with enhanced audio descriptions and how to interact with the world.
 
@@
 
+	\section{Related Work}
+	As digital games continuous to evolve making them more complex to play, accessibility becomes increasingly more important.
+	This section provides a deeper insight in related works that contributed to the understanding of how important accessibility in visual-centric digital games is.
+
+	\subsection{Themes of accessibility}
+	The paper \textcite{goncalves_my_2023} explores the strategies blind players use to play visual-centric mainstream games.
+	It analyzes over 70 hours of YouTube content from blind players to identify the strategies and methods they use to navigate and interact within games environments.
+
+	The study highlights that blind players often rely on audio cues to understand and navigate game environments.
+	They use repetitive actions like bumping into a wall to create a mental map of the environment.
+	Players also try to create landmarks by interacting with the game world, for example, by leaving enemies behind to know in which area they are at the moment.
+	This approach helps to navigate in game environments but also scare of new blind players due to frustration if the player become disorientated.
+
+	The result of their findings are seven themes focusing on describing strategies blind players created and adopted: (See \autoref{fig:seven-themes})
+
+	\begin{itemize}
+		\setlength\itemsep{0.5em}
+		\item Understanding the surroundings
+		\item Wayfnding in virtual environments
+		\item Dealing with perspective
+		\item Interacting with the world
+		\item Preparation, demand and cognitive load
+		\item Automation and difficulty
+		\item Playing with others
+	\end{itemize}
+
+	Additionally, \autoref{fig:seven-themes} shows us the existing barriers mainstream games have.
+
+	The paper also acknowledges the efforts of some game developers to make new and existing games more accessible to blind players.
+	This approach by developers is essential for reducing the accessibility gap in the upcoming years of game development.
+
+	\subsection{Inaccessibility in Games}
+	In 2008 \textcite{grammenos_game_2008} developed a game called \emph{Game Over!}, which is the first universally inaccessible game, created as an educational tool to teach game developers about accessibility guidelines.
+	This approach aimed to raise awareness and motivate game developers to make their games accessible for everyone.
+
+	The developed game \emph{Game Over!} has 21 levels implemented, each one violating a specific game accessibility guideline to frustrate but also educate by directly showing the developer what impact their design decisions have.
+	Some of the guidelines are:
+
+	\begin{itemize}
+		\setlength\itemsep{0.5em}
+		\item Require complex key combinations
+		\item Rapidly changing control schemes
+		\item Presenting information in inaccessible formats
+	\end{itemize}
+
+ 	Collected feedback from developers and players through surveys and public discussions indicate that the game raises awareness and educates about accessibility as intended.
+ 	It also suggested for the game to include direct access to additional information about each violated guideline, such as how specific accessibility can improve the game experience for disabled players.
+
+ 	The feedback also highlighted to add more levels to cover a wider range of accessibility guidelines which would add the potential to adapt the concept and further improve it as well as to highlight the importance of game design in digital games.
+
+	\subsection{Navigate a virtual environment using echolocation}
+	In 2018 \textcite{andrade_echo-house_2018} investigates the use of echolocation in a game environment to help blind players to navigate in them.
+	This approach aimed to investigate whether it is possible to create a \emph{virtual environment} (VE) where players can simulate echolocation to navigate and understand complex scenes within that VE.
+
+	Therefore, they developed a VE with Unity 5.6 and the SteamAudio plug-in.
+	This VE basically represents a three level house called \emph{Echo-House}, where users can navigate using sounds such as mouth-clicks, claps and footsteps, which generate echoes to receive information about the environment.
+	Each level had a goal players needed to reach to get to the next level of the house (See \autoref{fig:echo-house-layout}).
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[scale=0.5]{assets/echo-house-layout.png}
+		\caption{Layout of the three levels (Source: \textcite{andrade_echo-house_2018})}
+		\label{fig:echo-house-layout}
+	\end{figure}
+
+	The evaluation consists of a 45-minute playing session and a interview.
+	They found out that the echolocation provided the player with an improved sense of space within the VE.
+	However, challenges in orientation and mobility were still present which indicates the need of further support.
+
+	The paper highlighted the limitation of the study such as the small sample size and the need for further research to validate their findings.
+	Nevertheless, this paper gives important insight of what can be achieved with echolocation to help blind players.
+
 	\section{The Details}
@@
 	Firstly, we aim to explore previously mentioned developing problems, from universally accessible game design affecting diverse needs followed by technical challenges.
-	Secondly, we propose enhancements of already existing accessibility features in the theme environment navigating.
-	Lastly, we explore various types of feedback which are essential in enhancing of accessibility in digital games and focus on haptic feedback as well as further possibilities to use that to improve the experience in digital games for blind players.
+	Secondly, we explore various types of feedback which are essential in enhancing of accessibility in digital games and focus on haptic feedback as well as further possibilities to use that to improve the experience in digital games for blind players.
+	Lastly, we propose enhancements of already existing accessibility features and tools.
 
-	\subsection{Universally accessible game design}
-	%TODO
-	Test
+	\subsection{Universally Accessible Game Design}
+	In recent years, the awareness of accessible game design has been growing tremendously.
+	According to \emph{World Health Organization} \cite{world_health_organization_international_2004}, one out of ten persons has disabilities which often results in limitations in hearing, memory, vision or motor functions.
 
-	\subsection{Navigate a virtual environment using echolocation}
-	%TODO
-	Test
+	Digital games are getting more demanding in terms of the limitations we described before and this is where \emph{Universally Accessible Game Design} (UAGD) comes into play.
+	Through the implementation of UAGD, players with disabilities can benefit from features such as support for alternative input devices, including switches, eye-tracking systems, and mouth-operated controllers, which as a result can drastically enhance the game experience.
+	One of the key aspects is the implementation of settings that allow players to customize the features they need to improve their game experience.
+
+	We found a promising user-centered approach in the paper \textcite{grammenos_unified_2007} to apply UAGD in the development cycle of games.
+	The basic steps are summarized in \autoref{fig:universal-game-design-approach}, whereas an elaboration of these is provided in \textcite{grammenos_unified_2007}.
+
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[scale=0.5]{assets/universal-game-design-approach.png}
+		\caption{Applying UAGD (Source: \textcite{grammenos_unified_2007})}
+		\label{fig:universal-game-design-approach}
+	\end{figure}
 
@@
 	%TODO
-	Test
+	Combination with echolocation?
 
-	\section{Related Work}
-	Accessibility in visual-centric games is getting more important and the game industry have to keep up implementing them.
-	The research paper \textcite{goncalves_my_2023} has shown us that there are still major challenges to improve and further enhance existing accessibility features in various themes.
-	In 2008 \textcite{grammenos_game_2008} developed a game called \emph{Game Over!}, which is the first universally inaccessible game showing people how it is if a game is unplayable.
-	Additionally, in 2018 \textcite{andrade_echo-house_2018} described a new method to explore a virtual environment by using echolocation.
-	This section provides a deeper insight into these studies, how they approached the topic and what results they achieved.
-
-	\subsection{Echolocation in games}
-	Test
+	\subsection{Ways to improve existing accessibility features and tools}
+	%TODO
+	AI-tools?
 

### 2024-02-17 Paper/paper.tex
minor changes

@@
 
-    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visually-centric digital games are still a major challenge for blind players.
+    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visual-centric digital games are still a major challenge for blind players.
     In the following section we will delve deeper into some of the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.
@@
 	As digital games continuous to evolve making them more complex to play, accessibility becomes increasingly more important.
-	This section provides a deeper insight in related works that contributed to the understanding of how important accessibility in visual-centric digital games is.
+	This section provides a deeper insight into related work that has contributed to the understanding of the importance of accessibility in visual-centric digital games.
 
@@
 	The paper highlighted the limitation of the study such as the small sample size and the need for further research to validate their findings.
-	Nevertheless, this paper gives important insight of what can be achieved with echolocation to help blind players.
+	Nevertheless, this work provides an important insight into the possibilities of using echolocation to help blind players.
 

### 2024-02-18 Paper/paper.tex
improved Introduction and finished subsection "Universally Accessible Game Design"

@@
 
-	\section{Introduction}
+	\section{Introduction} \label{sec:introduction}
 	Today's accessible games for blind people are mainly games which are directly developed for them (\textcite{goncalves_my_2023}).
@@
 
-	So, the main idea of this paper is to give a broad insight of different and innovative accessibility features and tools, including haptic feedback and its ways to improve game experience which is a major technical challenge.
-	Additionally, this study explores design compromises and their associated problems as well as the need for standardization in the gaming industry developing games.
-	This raises two relevant research questions (RQ):
+	So, the main idea of this paper is to give a broad insight of \emph{Universally Accessible Game Design} (UAGD) which addresses the previously mentions developing problems.
+	Additionally, this study explores different and innovative accessibility features and tools, including haptic feedback and its ways to improve game experience which is a major technical challenge.
+
+	This raises following relevant research questions (RQ) which contributes to people playing visual-centric digital games:
 
@@
 		\setlength\itemsep{0.5em}
-		\item RQ1: Which innovative accessibility features and tools can enhance the gaming experience for blind players?
-		\item RQ2: In what ways can haptic feedback enhancements improve the game experience for blind players?
+		\item RQ1: How can UAGD improve the development of games with regard to accessibility?
+		\item RQ2: Which innovative accessibility features and tools can enhance the gaming experience for blind players?
+		\item RQ3: In what ways can haptic feedback enhancements improve the game experience for blind players?
 	\end{itemize}
-
-	%TODO
-	Contributions...
 
@@
 
-	\section{The Problem}
+	\section{The Problem} \label{sec:theProblem}
 	Blind players encounter many different barriers when playing visual-centric digital games which often rely greatly on graphical interfaces and visual cues. 
@@
 
-	\section{My Idea}
+	\section{My Idea} \label{sec:myIdea}
 	The gaming industry came a long way from no accessibility features and assistant tools at all to implementing more than 60 accessibility features in one game \cite{playstation_last_2020}.
@@
 
-	\section{Related Work}
+	\section{Related Work} \label{sec:relatedWork}
 	As digital games continuous to evolve making them more complex to play, accessibility becomes increasingly more important.
@@
 
-	\section{The Details}
+	\section{The Details} \label{sec:theDetails}
 	In this section, we delve into enhancing accessibility in digital games for blind players.
-	Firstly, we aim to explore previously mentioned developing problems, from universally accessible game design affecting diverse needs followed by technical challenges.
+	Firstly, we aim to explore previously mentioned developing problems in \autoref{sec:introduction}, from diverse needs and technical challenges followed by design compromises and standardization efforts.
 	Secondly, we explore various types of feedback which are essential in enhancing of accessibility in digital games and focus on haptic feedback as well as further possibilities to use that to improve the experience in digital games for blind players.
@@
 
-	Digital games are getting more demanding in terms of the limitations we described before and this is where \emph{Universally Accessible Game Design} (UAGD) comes into play.
-	Through the implementation of UAGD, players with disabilities can benefit from features such as support for alternative input devices, including switches, eye-tracking systems, and mouth-operated controllers, which as a result can drastically enhance the game experience.
-	One of the key aspects is the implementation of settings that allow players to customize the features they need to improve their game experience.
+	\subsubsection{Addressing Diverse Needs}
+	Digital games are getting more demanding in terms of limitations and this is where UAGD comes into play.
+	Through the implementation of UAGD, players with diverse needs can benefit from features such as support for alternative input devices, including switches, eye-tracking systems, and mouth-operated controllers, which as a result can drastically enhance the game experience.
+	By implementing these features, UAGD ensures that games are accessible to players with various disabilities, ensuring that games are enjoyable for a wider audience.
 
-	We found a promising user-centered approach in the paper \textcite{grammenos_unified_2007} to apply UAGD in the development cycle of games.
+	\subsubsection{Technical Challenges}
+	Implementing UAGD presents several technical challenges including compatibility with different hardware and the scalability of accessibility features.
+	By using a user-centered approach, as presented by \textcite{grammenos_unified_2007}, developers can integrate accessibility into the game development cycle and ensure that technical challenges are considered from the beginning of the project.
 	The basic steps are summarized in \autoref{fig:universal-game-design-approach}, whereas an elaboration of these is provided in \textcite{grammenos_unified_2007}.
@@
 	\end{figure}
+
+	\subsubsection{Design Compromises}
+	UAGD encourages developers to rethink design approaches, so that all players can enjoy the game they are developing.
+	This includes reimagining game mechanics, levels, and interfaces to ensure everyone gets the best game experience without destroying the games core idea.
+	The key here is to create games which are challenging and fun to play for all the players, regardless of their abilities.
+
+	\subsubsection{Standardization Efforts}
+	An important aspect of UAGD is to push towards standardizing accessibility features in all games.
+	To achieve that, common guidelines and best practices are needed, so that the gaming industry can create a more standardized approach to accessibility, making it easier for developers to implement these.
+	One key aspect here is to share those approaches and ideas with the software community as well as make the implementations open source.
+
+	In summary, UAGD is not just about making games playable for players with disabilities.
+	It should redefine how a game is developed and designed, so that the needs of all players are satisfied.
 

### 2024-02-18 Paper/paper.tex
Fully implemented section "The Details" and "Conclusions and Further Work"

@@
 
-	So, the main idea of this paper is to give a broad insight of \emph{Universally Accessible Game Design} (UAGD) which addresses the previously mentions developing problems.
+	So, the main idea of this paper is to give a broad insight of \emph{Universally Accessible Game Design} (UAGD) which addresses the previously mentioned developing problems.
 	Additionally, this study explores different and innovative accessibility features and tools, including haptic feedback and its ways to improve game experience which is a major technical challenge.
 
-	This raises following relevant research questions (RQ) which contributes to people playing visual-centric digital games:
+	This raises following relevant research questions (RQ) that contribute to blind people playing visual-centric digital games:
 
@@
 		\setlength\itemsep{0.5em}
-		\item RQ1: How can UAGD improve the development of games with regard to accessibility?
-		\item RQ2: Which innovative accessibility features and tools can enhance the gaming experience for blind players?
-		\item RQ3: In what ways can haptic feedback enhancements improve the game experience for blind players?
+		\item RQ1: How can UAGD improve the development of games with regard to accessibility? (\autoref{subsec:uagd})
+		\item RQ2: In what ways can haptic feedback enhancements improve the game experience for blind players? (\autoref{subsec:assistiveHapticFeedback})
+		\item RQ3: Which innovative accessibility features and tools can enhance the gaming experience for blind players? (\autoref{subsec:improvements})
 	\end{itemize}
@@
 	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_2020, playstation_last_2020-1}. 
-	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced.
+	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced (See \autoref{fig:tlou-accessibility-presets}).
+
+	\begin{figure*}[ht]
+		\centering
+		\includegraphics[scale=0.6,width=\textwidth]{assets/tlou-accessibility-presets.png}
+		\caption{Accessibility presets in TLOU2 (Source: \textcite{playstation_last_2020-1})}
+		\label{fig:tlou-accessibility-presets}
+	\end{figure*}
+
 	Additionally, \textcite{dale_last_2024} described that the game can be played all the way through with audio cues and navigation aids.
@@
 
+	In the past, video games were not designed with accessibility mind, which resulted in bad gaming experience for people with disabilities. 
+	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for blind players.
+
+	There are still many games which were not developed in a way that everyone can play it.
+	This paper aims to help to find a way to help the development of games as well as exploring existing accessibly features and ways to enhance them. 
+	By looking at what TLOU2 did and thinking about what else could be done, we can work towards making games a better experience for everyone.
+
 	\section{The Problem} \label{sec:theProblem}
-	Blind players encounter many different barriers when playing visual-centric digital games which often rely greatly on graphical interfaces and visual cues. 
-	To top that, the collection of those mainstream games have different perspectives such as top-down, first-person, and third-person views, where all three views give the player unique challenges in navigating game environment, understanding game objectives and interacting with in-game elements like players or objects.
+	Blind players encounter many different barriers when playing visual-centric digital games which often rely mainly on graphical interfaces and visual cues. 
+	Additionally, games have different perspectives such as top-down, first-person, and third-person views, where all three views give the player unique challenges in navigating within game environments, understanding game objectives and interacting with in-game elements like players or objects.
 	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) which still represent a great challenge for both players and developers.
@@
     To address the environment and pathfinding problems, one new technology was introduced in 2018 by \textcite{andrade_echo-house_2018} to use echolocation to explore a virtual environment which could drastically improve navigation in it.
-    As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or AI assistant tools could be a solution when developed and integration further.
-    Whereas the haptic feedback \cite{bello_haptics_2016} of for example PS5-Controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate when players aim too high or too low while an AI tool could provide the player with enhanced audio descriptions and how to interact with the world.
+    As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or \emph{Artificial Intelligence} (AI) tools could be a solution when developed and integrated further.
+    Whereas the haptic feedback \cite{bello_haptics_2016} of for example PS5-Controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate the environment they are walking on by adjusting the vibrations.
 
-    In summary, it can be said that the game industry already takes into account the most important accessibility features, yet most modern visual-centric digital games are still a major challenge for blind players.
-    In the following section we will delve deeper into some of the listed features above, their problems and possible solutions, as well as how to improve the overall experience of blind people.
+    The goal is to find an answer to the research question above by researching the field of UAGD, how to use haptic feedback to improve accessibility features and to find new ways to enhance existing accessibility features and tool in combination with AI.
+    Therefore, game developers should use the UAGD as a guide and ensure that all important accessibility features listed above are included in their games.
+
+    The following section provides a deeper insight into related work that has contributed to the understanding of the importance of accessibility in visual-centric digital games.
 
@@
 
-	The study highlights that blind players often rely on audio cues to understand and navigate game environments.
+	The study highlights that blind players often rely on audio cues to understand and navigate within game environments.
 	They use repetitive actions like bumping into a wall to create a mental map of the environment.
 	Players also try to create landmarks by interacting with the game world, for example, by leaving enemies behind to know in which area they are at the moment.
-	This approach helps to navigate in game environments but also scare of new blind players due to frustration if the player become disorientated.
+	This approach helps to navigate within game environments but also scare of new blind players due to frustration if the player become disorientated.
 
@@
 
-	\subsection{Universally Accessible Game Design}
+	\subsection{Universally Accessible Game Design} \label{subsec:uagd}
 	In recent years, the awareness of accessible game design has been growing tremendously.
@@
 	By using a user-centered approach, as presented by \textcite{grammenos_unified_2007}, developers can integrate accessibility into the game development cycle and ensure that technical challenges are considered from the beginning of the project.
-	The basic steps are summarized in \autoref{fig:universal-game-design-approach}, whereas an elaboration of these is provided in \textcite{grammenos_unified_2007}.
+	The basic steps are (See \autoref{fig:universal-game-design-approach}):
+
+	\begin{itemize}
+		\setlength\itemsep{0.5em}
+		\item Abstract task-based game design
+		\item Polymorphic specialization with design alternatives
+		\item Appropriateness analysis for the design alternatives
+		\item Compatibility analysis among design alternatives
+		\item Prototyping
+		\item Usability and accessibility evaluation
+	\end{itemize}
+
+	An elaboration of these steps is provided in \textcite{grammenos_unified_2007}
 
@@
 
-	\subsection{Assistive haptic feedback}
-	%TODO
-	Short introduction into feedback variants and where it is used "visual perception (sight), haptics (tactile) and aural (hearing)". \cite{kuber_towards_2007}
+	\subsection{Assistive haptic feedback} \label{subsec:assistiveHapticFeedback}
+	Assistive haptic feedback gets increasingly more important, especially in the gaming industry \cite{kuber_towards_2007}.
+	In this section we delve into innovative approaches to enhance the gaming experience for blind player through tactile technologies.
+	First we will give an overview of sensory perception which consists of visual (sight), haptic (tactile), and aural (hearing) as shown in \autoref{fig:sensory-perception}.
+	Then we will explore different possibilities to enhance game experience with haptic feedback.
 
-	\subsection{Further possibilities to use haptic feedback}
-	%TODO
-	Combination with echolocation?
+	\begin{figure}[ht]
+		\centering
+		\includegraphics[scale=0.4]{assets/sensory-perception.png}
+		\caption{Sensory perception (Source: \textcite{sanfilippo_perspective_2022})}
+		\label{fig:sensory-perception}
+	\end{figure}
 
-	\subsection{Ways to improve existing accessibility features and tools}
-	%TODO
-	AI-tools?
+	\subsubsection{Sensory Perception in Gaming for Blind Players}
+	Gaming experience for blind people primarily rely on non-visual sensory to navigated and interact within the game environment.
+	Visual perception which the player mainly get though sight, is often the primary interaction in most games.
+	However, for blind player, haptic and aural senses are the key.,
+
+	Haptic feedback is the sense of touch providing a physical response by vibration to the player \cite{chen_gamepad_2024, kuber_towards_2007, bello_haptics_2016}, which represent various action in a game like drawing a bow or shooting a weapon.
+	For example, a haptic glove could simulate the sensation of raindrops falling on a player's hand or the resistance encountered when pushing against an in-game object.
+
+	Aural feedback, in the other hand, provides sound to transfer information.
+	For example, the sound of footsteps can indicate that an ally or enemy is approaching, while footstep sounds changes indicate a transition from one area to another, such as moving from a city street into a quiet building.
+
+	\subsubsection{Enhancing Gaming Experience through Assistive Haptic Feedback}
+	Assistive haptic feedback helps blind players feel and interact with game worlds through touch.
+	This form of feedback offers a new dimension of immersion and accessibility.
+	For example, vibration can be designed in a way that they give information to the player by providing them with different vibration patterns on various surfaces such as uneven roads or a sandy beach.
+	By doing that, players receive a sense of location and movement within the game environment.
+
+	Beyond that, advanced haptic technologies like shape-changing interfaces or dynamic touch surfaces \cite{rasmussen_shape-changing_2012} can simulate more complex interactions.
+	These could include the sensation of touching sand or feel the resistance when drawing a bowstring by using a haptic glove mentioned previously.
+	This feedback technology could also help in navigating within a game environment where pulses could indicate the direction a player has to go.
+	This not only makes games more accessible to blind players but also increase the dimension of immersion for all players.
+
+	Considering the impact of standardizing this technology as a guideline within UAGD, making it a straightforward implementation for developers would help the game industry tremendously in terms of accessibility.
+
+	\subsection{Ways to improve existing accessibility features and tools} \label{subsec:improvements}
+	In this section we explore strategies to improve accessibility for blind players.
+	We are focusing us here on two promising advanced technology ideas:
+
+	\begin{itemize}
+		\setlength\itemsep{0.5em}
+		\item AI-Enhanced Testing and Audio Descriptions
+		\item Combining AI with echolocation techniques
+	\end{itemize}
+
+	\subsubsection{AI-Enhanced Testing and Audio Descriptions}
+	By implementing AI into the cycle of game development, we could significantly improve the accessibility for blind players by integration AI into the testing phase of the game.
+	After collecting enough data about accessibility, the AI could automate the testing phase, identifying accessibility issues or UAGD guideline violations which are not immediately visible for the developer.
+	This would ensure that games are designed the right way from the start.
+
+	Additionally, by letting the AI collect data during game play tests, it could generate real-time audio descriptions of game environments and action which could improve the gaming experience for blind players.
+	The generated descriptions can then customize for the needs of individual players.
+
+	To implement this method, additional research and testing are required.
+	This approach would greatly help developers in designing future games.
+
+	\subsubsection{Combining AI with Echolocation for Navigation}
+	Combining AI with echolocation technology could assist blind players in navigating within game environments.
+	The AI could interpret the echolocation signals which could be combined with haptic or aural feedback, helping players understand their environment.
+	For example, a glove or body armor as haptic feedback devices could receive the signals, process them to create a detailed map of the surroundings which provides the player with a much better understanding what is happening.
+
+	For this technology to be fully realized, further research like \textcite{andrade_echo-house_2018} is required.
+	This approach is promising for not only enhancing the experience for blind but all players.
 
 	\section{Conclusions and Further Work}
-	%TODO
-	A recap of the problem addressed and the proposed solution.
-	The implications of your research for the gaming industry and the broader accessibility community.
-	Any remaining challenges or unanswered questions that need to be addressed.
-	Suggestions for future research directions or enhancements to your proposed idea.
-	How your work contributes to advancing the state-of-the-art in accessibility technology for blind individuals playing digital games.
+	This paper addressed the challenge of enhancing accessibility features in digital games for blind players.
+	Our proposed solution is centered around \emph{Universally Accessible Game Design} (UAGD) and innovative assistive technologies like haptic feedback and echolocation.
+	This solution aims to improve the needs of blind players in current games.
+
+	\subsubsection{Conclusions}
+	Our findings offer answers to the proposed research questions, highlighting how UAGD (RQ1) can improve game development for better accessibility, how advancements in haptic feedback (RQ2) can significantly enhance the gaming experience not only for blind but all players and ways to improve existing accessibility features and tools (RQ3) by using AI.
+
+	\subsubsection{Further Work}
+	There are still open challenges such as the full integration of echolocation techniques as well as additional research in using AI in testing phases and audio description generation.
+	Future studies should focus on the echolocation technology for gaming, exploring AI in creating dynamic audio descriptions and identifying missing accessibility features, and developing more haptic feedback systems.
+
+	Our study opens the door to new possibilities in making digital gaming and development a better experience, ensuring that advancements in gaming technology can be enjoyed by everyone, including those who are blind.
 

### 2024-02-18 Paper/paper.tex
minor text changes

@@
 	In the past, video games were not designed with accessibility mind, which resulted in bad gaming experience for people with disabilities. 
-	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for blind players.
+	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for disabled players.
 
-	There are still many games which were not developed in a way that everyone can play it.
-	This paper aims to help to find a way to help the development of games as well as exploring existing accessibly features and ways to enhance them. 
-	By looking at what TLOU2 did and thinking about what else could be done, we can work towards making games a better experience for everyone.
+	However, there are still many games which were not developed in a way that everyone can play it.
+	With focus on blind players, this paper aims to find a way to help the development cycle of games as well as exploring existing accessibly features and ways to enhance them.
 

### 2024-02-18 Paper/paper.tex
improved section "The Problem"

@@
 	Additionally, games have different perspectives such as top-down, first-person, and third-person views, where all three views give the player unique challenges in navigating within game environments, understanding game objectives and interacting with in-game elements like players or objects.
+
+	Popular games, such as \emph{The Legend of Zelda} rely mainly on visuals.
+	For blind players, this is obviously a big problem because they miss a lot of important information on how to complete tasks or what is happening around them.
+
+	As \textcite{goncalves_my_2023} states, players express feelings of frustration, telling their viewers the need for more and better accessibility features, so that everyone including blind players can have a great game experience.
+
 	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) which still represent a great challenge for both players and developers.
-	%TODO rewrite
 
@@
 
-	\autoref{fig:seven-themes} gives a great overview what accessibility features and assistant tools are still missing and in which direction the gaming industry should focus.
+	\autoref{fig:seven-themes} gives a great overview what accessibility features are still missing and in which direction the gaming industry should focus.
 

### 2024-02-18 Paper/paper.tex
minor improvements

@@
 
-	In the past, video games were not designed with accessibility mind, which resulted in bad gaming experience for people with disabilities. 
+	In the past, video games were not designed with accessibility in mind, which resulted in bad gaming experience for people with disabilities. 
 	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for disabled players.
@@
 
-	\subsubsection{Conclusions}
+	\subsection{Conclusion}
 	Our findings offer answers to the proposed research questions, highlighting how UAGD (RQ1) can improve game development for better accessibility, how advancements in haptic feedback (RQ2) can significantly enhance the gaming experience not only for blind but all players and ways to improve existing accessibility features and tools (RQ3) by using AI.
 
-	\subsubsection{Further Work}
+	\subsection{Further Work}
 	There are still open challenges such as the full integration of echolocation techniques as well as additional research in using AI in testing phases and audio description generation.

### 2024-02-18 Paper/paper.tex
implemented feedback, added abstract and changed title

@@
 	%% allowing the author to define a "short title" to be used in page headers.
-	\title{Assistant Tools and Accessibility Features for Blind People Playing Visual-Centric Digital Games}
+	\title{Accessible Game Design: Exploring Innovative Technologies for Blind Players}
 
@@
 	\begin{abstract}
-		Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi
-		malesuada, quam in pulvinar varius, metus nunc fermentum urna, id
-		sollicitudin purus odio sit amet enim. Aliquam ullamcorper eu ipsum
-		vel mollis. Curabitur quis dictum nisl. Phasellus vel semper risus, et
-		lacinia dolor. Integer ultricies commodo sem nec semper.
+		The paper focuses on enhancing digital game accessibility for blind players through Universally Accessible Game Design and assistive technologies like haptic feedback and echolocation.
+		It aims to improve game accessibility and experience for blind players by addressing game development challenges for inclusivity.
+		The paper suggests further research on integrating echolocation, AI for testing and audio descriptions, and developing more advanced haptic feedback systems to make gaming more inclusive and enjoyable for all, including those with disabilities.
 	\end{abstract}
@@
 	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_2020, playstation_last_2020-1}. 
-	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced (See \autoref{fig:tlou-accessibility-presets}).
+	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced.
+
+	Additionally, \textcite{dale_last_2024} described that the game can be played all the way through with audio cues and navigation aids.
+	It includes preset accessibility options, as shown in \autoref{fig:tlou-accessibility-presets}, for common disabilities such as hearing or vision impairments.
+	It also introduces accessibility menus when the game is first started, making it easier for players with disabilities to adjust settings.
+	To top that, \emph{Naughty Dog} released a remastered version of TLOU2 in 2024 with a reworked \emph{Cinematic Audio Descriptions} feature \cite{playstation_last_2024}.
 
@@
 
-	Additionally, \textcite{dale_last_2024} described that the game can be played all the way through with audio cues and navigation aids.
-	It includes preset accessibility options for common disabilities like hearing or vision impairments. 
-	It also introduces accessibility menus when the game is first started, making it easier for players with disabilities to adjust settings.
-	To top that, \emph{Naughty Dog} released a remastered version of TLOU2 in 2024 with a reworked \emph{Cinematic Audio Descriptions} feature \cite{playstation_last_2024}.
-
 	In the past, video games were not designed with accessibility in mind, which resulted in bad gaming experience for people with disabilities. 
@@
 
-	However, there are still many games which were not developed in a way that everyone can play it.
-	With focus on blind players, this paper aims to find a way to help the development cycle of games as well as exploring existing accessibly features and ways to enhance them.
+	However, there are still many games that have not been developed in a way that everyone can play them.
+	With a focus on blind players, this paper aims to find a way to support the development cycle of games as well as explore existing accessibly features and ways to improve them.
 
@@
     As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or \emph{Artificial Intelligence} (AI) tools could be a solution when developed and integrated further.
-    Whereas the haptic feedback \cite{bello_haptics_2016} of for example PS5-Controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate the environment they are walking on by adjusting the vibrations.
+    Whereas the haptic feedback \cite{bello_haptics_2016} of for example \emph{PlayStation 5} (PS5) controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate the environment they are walking on by adjusting the vibrations.
 
@@
 	\section{Related Work} \label{sec:relatedWork}
-	As digital games continuous to evolve making them more complex to play, accessibility becomes increasingly more important.
+	As digital games continue to evolve making them more complex to play, accessibility becomes increasingly more important.
 	This section provides a deeper insight into related work that has contributed to the understanding of the importance of accessibility in visual-centric digital games.
@@
  	Collected feedback from developers and players through surveys and public discussions indicate that the game raises awareness and educates about accessibility as intended.
- 	It also suggested for the game to include direct access to additional information about each violated guideline, such as how specific accessibility can improve the game experience for disabled players.
+ 	It was also suggested to include direct access to additional information about each violated guideline, such as how specific accessibility can improve the game experience for disabled players.
 
@@
 	\subsection{Navigate a virtual environment using echolocation}
-	In 2018 \textcite{andrade_echo-house_2018} investigates the use of echolocation in a game environment to help blind players to navigate in them.
+	In 2018 \textcite{andrade_echo-house_2018} investigates the use of echolocation to help blind players to navigate within a game environment.
 	This approach aimed to investigate whether it is possible to create a \emph{virtual environment} (VE) where players can simulate echolocation to navigate and understand complex scenes within that VE.
@@
 	In recent years, the awareness of accessible game design has been growing tremendously.
-	According to \emph{World Health Organization} \cite{world_health_organization_international_2004}, one out of ten persons has disabilities which often results in limitations in hearing, memory, vision or motor functions.
+	According to the \emph{World Health Organization} \cite{world_health_organization_international_2004}, one out of ten persons has disabilities which often results in limitations in hearing, memory, vision or motor functions.
 
@@
 	To achieve that, common guidelines and best practices are needed, so that the gaming industry can create a more standardized approach to accessibility, making it easier for developers to implement these.
-	One key aspect here is to share those approaches and ideas with the software community as well as make the implementations open source.
+	One key aspect of this is sharing these approaches and ideas with the software community as well as making the implementations open source.
 
@@
 	\subsubsection{Sensory Perception in Gaming for Blind Players}
-	Gaming experience for blind people primarily rely on non-visual sensory to navigated and interact within the game environment.
+	Gaming experience for blind people primarily rely on non-visual sensory to navigate and interact within the game environment.
 	Visual perception which the player mainly get though sight, is often the primary interaction in most games.
-	However, for blind player, haptic and aural senses are the key.,
+	However, for blind players, haptic and aural senses are the key.,
 
-	Haptic feedback is the sense of touch providing a physical response by vibration to the player \cite{chen_gamepad_2024, kuber_towards_2007, bello_haptics_2016}, which represent various action in a game like drawing a bow or shooting a weapon.
+	Haptic feedback is the sense of touch providing a physical response by vibration to the player \cite{chen_gamepad_2024, kuber_towards_2007, bello_haptics_2016}, which represent various actions in a game like drawing a bow or shooting a weapon.
 	For example, a haptic glove could simulate the sensation of raindrops falling on a player's hand or the resistance encountered when pushing against an in-game object.
@@
 	\subsubsection{AI-Enhanced Testing and Audio Descriptions}
-	By implementing AI into the cycle of game development, we could significantly improve the accessibility for blind players by integration AI into the testing phase of the game.
+	By implementing AI into the cycle of game development, we could significantly improve the accessibility for blind players by integrating AI into the testing phase of the game.
 	After collecting enough data about accessibility, the AI could automate the testing phase, identifying accessibility issues or UAGD guideline violations which are not immediately visible for the developer.
@@
 
-	Our study opens the door to new possibilities in making digital gaming and development a better experience, ensuring that advancements in gaming technology can be enjoyed by everyone, including those who are blind.
+	Our study opens the door to new opportunities to make digital games and their development a better experience and to ensure that advancements in gaming technology can be enjoyed by everyone, including those with disabilities.
 

### 2024-02-19 Paper/paper.tex
Minor corrections, ready for submission

@@
 	%% article.
-	%TODO
 	\begin{abstract}
@@
 	\section{Introduction} \label{sec:introduction}
-	Today's accessible games for blind people are mainly games which are directly developed for them (\textcite{goncalves_my_2023}).
-	While these games are enjoyable, mainstream games are a serious challenge for blind people because they consist of complex environments, mechanics and interactions with \emph{Non-Player Character} (NPC) players or even real players in \emph{Player versus player} (PvP) games.
+	Today's accessible games for blind players are mainly games that are developed directly for them \cite{goncalves_my_2023}.
+	While these games are enjoyable, mainstream games are a serious challenge for blind players because they consist of complex environments, mechanics and interactions with \emph{Non-Player Character} (NPC) players or even real players in \emph{Player versus player} (PvP) games.
 
@@
 
-	So, the main idea of this paper is to give a broad insight of \emph{Universally Accessible Game Design} (UAGD) which addresses the previously mentioned developing problems.
-	Additionally, this study explores different and innovative accessibility features and tools, including haptic feedback and its ways to improve game experience which is a major technical challenge.
+	So, the main idea of this paper is to give a broad insight into \emph{Universally Accessible Game Design} (UAGD), which addresses the previously mentioned developing problems.
+	Additionally, this study explores different and innovative accessibility features and tools, including haptic feedback and its ways to improve game experience, which is a major technical challenge.
 
-	This raises following relevant research questions (RQ) that contribute to blind people playing visual-centric digital games:
+	This raises following relevant research questions (RQ) that contribute to blind players playing visual-centric digital games:
 
@@
 	\subsection{Motivation}
-	One big step forward making mainstream games more accessible for blind people was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_2020, playstation_last_2020-1}. 
+	One big step forward making mainstream games more accessible for blind players was the game \emph{The Last of Us Part II} (TLOU2) \cite{playstation_last_2020, playstation_last_2020-1}. 
 	According to \textcite{leite_extended_2021} the game company \emph{Naughty Dog} implemented more than 60 accessibility features and is considered as the most accessible game ever produced.
@@
 	In the past, video games were not designed with accessibility in mind, which resulted in bad gaming experience for people with disabilities. 
-	However, over time, game companies started to develop and include accessibility features in their games which significantly improved the game experience for disabled players.
+	Over time, however, game companies began to develop and include accessibility features in their games, significantly improving the gaming experience for disabled players.
 
-	However, there are still many games that have not been developed in a way that everyone can play them.
+	Nevertheless, there are still many games that have not been developed in a way that everyone can play them.
 	With a focus on blind players, this paper aims to find a way to support the development cycle of games as well as explore existing accessibly features and ways to improve them.
@@
 	\section{The Problem} \label{sec:theProblem}
-	Blind players encounter many different barriers when playing visual-centric digital games which often rely mainly on graphical interfaces and visual cues. 
+	Blind players encounter many different barriers when playing visual-centric digital games, which often rely mainly on graphical interfaces and visual cues. 
 	Additionally, games have different perspectives such as top-down, first-person, and third-person views, where all three views give the player unique challenges in navigating within game environments, understanding game objectives and interacting with in-game elements like players or objects.
@@
 
-	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) which still represent a great challenge for both players and developers.
+	Building on that, the authors of \textcite{goncalves_my_2023} have categorized seven themes and identified unresolved barriers (see \autoref{fig:seven-themes}) that still represent a great challenge for both players and developers.
 
@@
 	The gaming industry came a long way from no accessibility features and assistant tools at all to implementing more than 60 accessibility features in one game \cite{playstation_last_2020}.
-	According to research papers \cite{goncalves_my_2023, grammenos_designing_2009, grammenos_game_2008, araujo_mobile_2017} some of the most important accessibility features for blind people in visual-centric games include:
+	According to research papers \cite{goncalves_my_2023, grammenos_designing_2009, grammenos_game_2008, araujo_mobile_2017} some of the most important accessibility features for blind players in visual-centric games include:
 
@@
 
-    To address the environment and pathfinding problems, one new technology was introduced in 2018 by \textcite{andrade_echo-house_2018} to use echolocation to explore a virtual environment which could drastically improve navigation in it.
+    To address the environment and pathfinding problems, one new technology was introduced in 2018 by \textcite{andrade_echo-house_2018} to use echolocation to explore a virtual environment, which could drastically improve navigation in it.
     As for perspective (camera) and interacting with the world, hardware solutions like haptic feedback or \emph{Artificial Intelligence} (AI) tools could be a solution when developed and integrated further.
-    Whereas the haptic feedback \cite{bello_haptics_2016} of for example \emph{PlayStation 5} (PS5) controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024} could indicate the environment they are walking on by adjusting the vibrations.
+    Whereas the haptic feedback \cite{bello_haptics_2016} of, for example \emph{PlayStation 5} (PS5) controllers \cite{akyaman_anticipated_2021, chen_gamepad_2024}, could indicate the environment they are walking on by adjusting the vibrations.
 
@@
     Therefore, game developers should use the UAGD as a guide and ensure that all important accessibility features listed above are included in their games.
-
-    The following section provides a deeper insight into related work that has contributed to the understanding of the importance of accessibility in visual-centric digital games.
 
@@
 
- 	The feedback also highlighted to add more levels to cover a wider range of accessibility guidelines which would add the potential to adapt the concept and further improve it as well as to highlight the importance of game design in digital games.
+ 	The feedback also highlighted to add more levels to cover a wider range of accessibility guidelines, which would add the potential to adapt the concept and further improve it as well as to highlight the importance of game design in digital games.
 
@@
 
-	The evaluation consists of a 45-minute playing session and a interview.
+	The evaluation consists of a 45-minute playing session followed by an interview.
 	They found out that the echolocation provided the player with an improved sense of space within the VE.
-	However, challenges in orientation and mobility were still present which indicates the need of further support.
+	However, challenges in orientation and mobility were still present, which indicates the need of further support.
 
@@
 	Firstly, we aim to explore previously mentioned developing problems in \autoref{sec:introduction}, from diverse needs and technical challenges followed by design compromises and standardization efforts.
-	Secondly, we explore various types of feedback which are essential in enhancing of accessibility in digital games and focus on haptic feedback as well as further possibilities to use that to improve the experience in digital games for blind players.
+	Secondly, we explore various types of feedback, which are essential in enhancing of accessibility in digital games and focus on haptic feedback as well as further possibilities to use that to improve the experience in digital games for blind players.
 	Lastly, we propose enhancements of already existing accessibility features and tools.
@@
 	In recent years, the awareness of accessible game design has been growing tremendously.
-	According to the \emph{World Health Organization} \cite{world_health_organization_international_2004}, one out of ten persons has disabilities which often results in limitations in hearing, memory, vision or motor functions.
+	According to the \emph{World Health Organization} \cite{world_health_organization_international_2004}, one out of ten persons has disabilities, which often results in limitations in hearing, memory, vision or motor functions.
 
@@
 
-	An elaboration of these steps is provided in \textcite{grammenos_unified_2007}
+	An elaboration of these steps is provided in \textcite{grammenos_unified_2007}.
 
@@
 	UAGD encourages developers to rethink design approaches, so that all players can enjoy the game they are developing.
-	This includes reimagining game mechanics, levels, and interfaces to ensure everyone gets the best game experience without destroying the games core idea.
-	The key here is to create games which are challenging and fun to play for all the players, regardless of their abilities.
+	This includes reimagining game mechanics, levels, and interfaces to ensure everyone gets the best game experience without destroying the game's core idea.
+	The key here is to create games that are challenging and fun for all players, regardless of their abilities.
 
@@
 	In this section we delve into innovative approaches to enhance the gaming experience for blind player through tactile technologies.
-	First we will give an overview of sensory perception which consists of visual (sight), haptic (tactile), and aural (hearing) as shown in \autoref{fig:sensory-perception}.
+	First, we will give an overview of sensory perception which consists of visual (sight), haptic (tactile), and aural (hearing) as shown in \autoref{fig:sensory-perception}.
 	Then we will explore different possibilities to enhance game experience with haptic feedback.
@@
 	\subsubsection{Sensory Perception in Gaming for Blind Players}
-	Gaming experience for blind people primarily rely on non-visual sensory to navigate and interact within the game environment.
-	Visual perception which the player mainly get though sight, is often the primary interaction in most games.
-	However, for blind players, haptic and aural senses are the key.,
+	Visual perception, which the player mainly get though sight, is often the primary interaction in most games.
+	However, for blind players, haptic and aural senses are the key.
 
-	Haptic feedback is the sense of touch providing a physical response by vibration to the player \cite{chen_gamepad_2024, kuber_towards_2007, bello_haptics_2016}, which represent various actions in a game like drawing a bow or shooting a weapon.
+	Haptic feedback is the sense of touch providing a physical response by vibration to the player \cite{chen_gamepad_2024, kuber_towards_2007, bello_haptics_2016}, which represent various actions in a game like drawing a bowstring or shooting a weapon.
 	For example, a haptic glove could simulate the sensation of raindrops falling on a player's hand or the resistance encountered when pushing against an in-game object.
@@
 	These could include the sensation of touching sand or feel the resistance when drawing a bowstring by using a haptic glove mentioned previously.
-	This feedback technology could also help in navigating within a game environment where pulses could indicate the direction a player has to go.
-	This not only makes games more accessible to blind players but also increase the dimension of immersion for all players.
+	This feedback technology could also help in navigating within a game environment, where pulses could indicate the direction a player has to go.
+	This not only makes games more accessible to blind players, but also increase the dimension of immersion for all players.
 
@@
 	\subsubsection{AI-Enhanced Testing and Audio Descriptions}
-	By implementing AI into the cycle of game development, we could significantly improve the accessibility for blind players by integrating AI into the testing phase of the game.
-	After collecting enough data about accessibility, the AI could automate the testing phase, identifying accessibility issues or UAGD guideline violations which are not immediately visible for the developer.
+	By implementing AI into the cycle of game development, we could significantly improve the accessibility for blind players by integrating it into the testing phase of the game.
+	After collecting enough data about accessibility, the AI could automate the testing phase, identifying accessibility issues or UAGD guideline violations that are not immediately visible to the developer.
 	This would ensure that games are designed the right way from the start.
 
-	Additionally, by letting the AI collect data during game play tests, it could generate real-time audio descriptions of game environments and action which could improve the gaming experience for blind players.
-	The generated descriptions can then customize for the needs of individual players.
+	Additionally, by letting the AI collect data during game play tests, it could generate real-time audio descriptions of game environments and player actions which could improve the gaming experience for blind players.
+	The generated descriptions can then be customized to the needs of individual players.
 
@@
 	Combining AI with echolocation technology could assist blind players in navigating within game environments.
-	The AI could interpret the echolocation signals which could be combined with haptic or aural feedback, helping players understand their environment.
+	The AI could interpret the echolocation signals, which could be combined with haptic or aural feedback, helping players understand their environment.
 	For example, a glove or body armor as haptic feedback devices could receive the signals, process them to create a detailed map of the surroundings which provides the player with a much better understanding what is happening.
@@
 	\subsection{Conclusion}
-	Our findings offer answers to the proposed research questions, highlighting how UAGD (RQ1) can improve game development for better accessibility, how advancements in haptic feedback (RQ2) can significantly enhance the gaming experience not only for blind but all players and ways to improve existing accessibility features and tools (RQ3) by using AI.
+	Our findings offer answers to the proposed research questions, highlighting how UAGD (RQ1) can improve game development for better accessibility, how advancements in haptic feedback (RQ2) can significantly enhance the gaming experience for everyone and ways to improve existing accessibility features and tools (RQ3) by using AI.
 
 	\subsection{Further Work}
-	There are still open challenges such as the full integration of echolocation techniques as well as additional research in using AI in testing phases and audio description generation.
+	There are still open challenges, such as the full integration of echolocation techniques, and further research is needed on the use of AI in test phases and the creation of audio descriptions.
 	Future studies should focus on the echolocation technology for gaming, exploring AI in creating dynamic audio descriptions and identifying missing accessibility features, and developing more haptic feedback systems.

### 2024-02-19 Paper/paper.tex
Updated Abstract

@@
 	\begin{abstract}
-		The paper focuses on enhancing digital game accessibility for blind players through Universally Accessible Game Design and assistive technologies like haptic feedback and echolocation.
-		It aims to improve game accessibility and experience for blind players by addressing game development challenges for inclusivity.
-		The paper suggests further research on integrating echolocation, AI for testing and audio descriptions, and developing more advanced haptic feedback systems to make gaming more inclusive and enjoyable for all, including those with disabilities.
+		Accessibility in games is important to ensure that everyone, including people with disabilities, can enjoy gaming.
+		In this paper, we discuss the importance of Universally Accessible Game Design and introduce innovative technologies such as haptic feedback that improve the gaming experience for blind players.
+		We address the challenges developers face in making games accessible and explore solutions to improve existing accessibility features with the help of advanced technologies.
+		This research aims to make digital games more inclusive, highlighting the importance of accessibility in the gaming industry.
 	\end{abstract}
